

---
title: "Ranking of Benchmark Pipelines"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## {.tabset}

### TWGBS
#### Distance Plot summary
```{r, results = 'asis', echo = F, out.width = "100%", fig.cap = "TWGBS"}
knitr::include_graphics("/Users/lilianleiter/Desktop/Bioinfo/TWGBS_DistPlot_sum_absolute.pdf")
```
#### Rankings
##### Ranking by Sample
##### {.tabset}
###### 5T
```{r, results='asis', echo =FALSE}
TWGBS_5T <- read.csv("~/Desktop/Bioinfo/TWGBS_5T")
knitr::kable(head(TWGBS_5T), format = "markdown")
```
###### 5N
```{r, results='asis', echo =FALSE}
TWGBS_5N <- read.csv("~/Desktop/Bioinfo/TWGBS_5N")
knitr::kable(head(TWGBS_5N), format = "markdown")
```
###### 6T
```{r, results='asis', echo =FALSE}
TWGBS_6T <- read.csv("~/Desktop/Bioinfo/TWGBS_6T")
knitr::kable(head(TWGBS_6T), format = "markdown")
```
###### 6N
```{r, results='asis', echo =FALSE}
TWGBS_6N <- read.csv("~/Desktop/Bioinfo/TWGBS_6N")
knitr::kable(head(TWGBS_6N), format = "markdown")
```
###### Summary Ranking
```{r, results='asis', out.width = "100%", fig.width = 4, fig.height= 12, echo =FALSE}
TWGBS_Sample_sum <- read.csv("~/Desktop/Bioinfo/TWGBS_Sample_sum")
knitr::kable(head(TWGBS_Sample_sum[1:12, ]), format = "markdown")
```
##### Ranking by Type
##### {.tabset}
###### N
```{r, results='asis', echo =FALSE}
TWGBS_N <- read.csv("~/Desktop/Bioinfo/TWGBS_N")
# xtable::xtable(x= TWGBS_N, type = "html")
library(xtable)
print(xtable(TWGBS_N), type = "html")
# knitr::kable(head(TWGBS_N), format = "markdown")
```

###### T
```{r, results='asis', echo=FALSE}
# bsmadez::rankings()
# TWGBS_T <- TWGBS_5T <- rankings$ranking_by_sample[rankings$ranking_by_sample$method == "TWGBS" & rankings$ranking_by_sample$sample == "5T",]
TWGBS_T <- read.csv("~/Desktop/Bioinfo/TWGBS_T")
knitr::kable(head(TWGBS_T), format = "markdown")
```
###### Summary Ranking
```{r, results='asis', echo =FALSE}
TWGBS_Type_sum <- read.csv("~/Desktop/Bioinfo/TWGBS_Type_sum")
knitr::kable(head(TWGBS_Type_sum), format = "markdown")
```
##### Ranking by Method
##### {.tabset}
###### Full Ranking
```{r, results='asis', echo =FALSE}
TWGBS_full <- read.csv("~/Desktop/Bioinfo/TWGBS_full")
knitr::kable(head(TWGBS_full), format = "markdown")
```
###### Summary Ranking
```{r, results='asis', echo =FALSE}
TWGBS_sum <- read.csv("~/Desktop/Bioinfo/TWGBS_sum")
knitr::kable(head(TWGBS_sum), format = "markdown")
```
##### Final Summary Ranking
```{r, results='asis', echo =FALSE}
TWGBS_final_sum <- read.csv("~/Desktop/Bioinfo/TWGBS_final_sum")
library(xtable)
print(xtable(TWGBS_final_sum), type = "html", align = "l", digits = 6, display = "s", auto= T, size = Huge)
# knitr::kable(head(TWGBS_final_sum), format = "markdown")
```
### WGBS
#### Distance Plot summary
```{r, results = 'asis', echo = F, out.width = "100%", fig.cap = "WGBS"}
knitr::include_graphics("/Users/lilianleiter/Desktop/Bioinfo/WGBS_DistPlot_sum_absolute.pdf")
```
#### Rankings
##### Ranking by Sample
#####{.tabset}
###### 5T
```{r, results='asis', echo =FALSE}
WGBS_5T <- read.csv("~/Desktop/Bioinfo/WGBS_5T")
knitr::kable(head(WGBS_5T), format = "markdown")
```
###### 5N
```{r, results='asis', echo =FALSE}
WGBS_5N <- read.csv("~/Desktop/Bioinfo/WGBS_5N")
knitr::kable(head(WGBS_5N), format = "markdown")
```
###### 6T
```{r, results='asis', echo =FALSE}
WGBS_6T <- read.csv("~/Desktop/Bioinfo/WGBS_6T")
knitr::kable(head(WGBS_6T), format = "markdown")
```
###### 6N
```{r, results='asis', echo =FALSE}
WGBS_6N <- read.csv("~/Desktop/Bioinfo/WGBS_6N")
knitr::kable(head(WGBS_6N), format = "markdown")
```
###### Summary Ranking
```{r, results='asis', echo =FALSE}
WGBS_Sample_sum <- read.csv("~/Desktop/Bioinfo/WGBS_Sample_sum")
knitr::kable(head(WGBS_Sample_sum), format = "markdown")
```
##### Ranking by Type
##### {.tabset}
###### N
```{r, results='asis', echo =FALSE}
WGBS_N <- read.csv("~/Desktop/Bioinfo/WGBS_N")
knitr::kable(head(WGBS_N), format = "markdown")
```

###### T
```{r, results='asis', echo=FALSE}
# bsmadez::rankings()
# WGBS_T <- WGBS_5T <- rankings$ranking_by_sample[rankings$ranking_by_sample$method == "WGBS" & rankings$ranking_by_sample$sample == "5T",]
WGBS_T <- read.csv("~/Desktop/Bioinfo/WGBS_T")
knitr::kable(head(WGBS_T), format = "markdown")
```
###### Summary Ranking
```{r, results='asis', echo =FALSE}
WGBS_Type_sum <- read.csv("~/Desktop/Bioinfo/WGBS_Type_sum")
knitr::kable(head(WGBS_Type_sum), format = "markdown")
```
##### Ranking by Method
##### {.tabset}
###### Full Ranking
```{r, results='asis', echo =FALSE}
WGBS_full <- read.csv("~/Desktop/Bioinfo/WGBS_full")
knitr::kable(head(WGBS_full), format = "markdown")
```
###### Summary Ranking
```{r, results='asis', echo =FALSE}
WGBS_sum <- read.csv("~/Desktop/Bioinfo/WGBS_sum")
knitr::kable(head(WGBS_sum), format = "markdown")
```
##### Final Summary Ranking
```{r, results='asis', echo =FALSE}
WGBS_final_sum <- read.csv("~/Desktop/Bioinfo/WGBS_final_sum")
knitr::kable(head(WGBS_final_sum), format = "markdown")
```
